\chapter	{Kolmogorov Extension Theorem}

Let \( S^\alpha \) be a directed family of Hausdorff spaces,
indexed by \( \alpha \in A \).
Suppose that $\mu^\alpha$ is
an inner-regular probability measure on~$S^\alpha$,
such that the maps \( p_\beta^\alpha \colon S^\beta \to S^\alpha \)
for \( \beta \ge \alpha \)
preserve the measures,
in that \( p_\beta^\alpha(\mu^\beta) = \mu^\alpha \).
Finally, suppose that the~$p_\beta^\alpha$ are surjections.
Let \( S^A = \projlim_\alpha S^\alpha \)
be the projective limit in the category of measurable spaces,
with projections \( p^\alpha = p_A^\alpha \colon S^A \to S^\alpha \).
\begin	{theorem}[Kolmogorov Extension]
\label	{thm:kolmogorov-extension}
There exists a unique probability measure~$P$ on~$S^A$
such that \( p^\alpha(P) = \mu^\alpha \).
\end	{theorem}

\begin	{lemma}
\label	{lem:CH-projlim}
Let \( X^J = \lim_{j \in J} X^j \)
be a filtered limit of compact Hausdorff spaces.
Then $X^J$ is compact Hausdorff,
and if \( X^j \ne \emptyset \) then \( X^J \ne \emptyset \).
\end	{lemma}
\begin	{proof}
For \( f \colon j \to j' \) in~$J$,
let \( F_f = \{\, \mathbf x \in \prod_{j \in J} X^j
\mid f \cdot \mathbf x_j = \mathbf x_{j'} \,\} \).
In the product topology,
\( F_f \subseteq \prod_{j \in J} X^j \) is closed.
Thus \( X^J \cong \bigcap_{f \in J} F_f \) is closed, compact, and Hausdorff.

Suppose that \( x^j \in X^j \) for every \( j \in J \).
Since \( \prod_{f \in J} X^j \) is compact by Tychonoff's theorem,
it suffices to show for any finite subcategory \( K \subseteq J \)
that \( \bigcap_{f \in K} F_f \ne \emptyset \).
Since $J$ is filtering,
$K$ admits a cone \( f_j \colon j_K \to j \), \( j \in K \).
Setting \( \mathbf x_j = f_j \cdot x^{j_K} \) if \( j \in K \)
and \( \mathbf x_j = x^j \) otherwise,
\( \mathbf x \in \bigcap_{f \in K} F_f \).
\end	{proof}

\begin	{corollary}
\label	{cor:surjective-projections}
Suppose \( X^J = \lim_{j \in J} X^j \) is a filtered limit
of compact Hausdorff spaces,
where all involved maps between the~$X^j$ are surjective.
Then every projection \( X^J \to X^j \) is a surjection.
\end	{corollary}
\begin	{proof}
Let \( x^{j_0} \in X^{j_0} \),
and apply the lemma replacing~$X^j$
by the set of~$x^j$ for which \( f \cdot x^j = x^{j_0} \)
for all \( f \colon j \to j_0 \).
%by \( \bigcap_{f \colon j \to j_0} \{\, x^j \in X^j
%\mid f \cdot x^j = x^{j_0} \,\} \).
\end	{proof}

Let \( \Sigma^A_0 = \bigcup_\alpha \sgen(p^\alpha) \).
This is an algebra because the union is directed:
if \( \alpha \ge \beta \)
then \( \sgen(p^\alpha) = \sgen(p^\alpha_\beta p^\beta)
\subseteq \sgen(p^\beta) \).
%TODO compactification
%TODO lettering
An event \( A^A_0 \in \Sigma^A_0 \)
is of the form \( A^A_0 = \{ p^\alpha \in A^\alpha \} \).
Note that if \( \alpha,\beta \in A \)
and \( \{ p^\alpha \in A^\alpha \} = \{ p^\beta \in A^\beta \} \),
then for \( \gamma \ge \alpha,\beta \)
we have
\( (p^\gamma)^* \{ p^\alpha_\gamma \in A^\alpha \}
=  (p^\gamma)^* \{ p^\beta _\gamma \in A^\beta  \}
\),
and because $p^\gamma$ is surjective
by \autoref{cor:surjective-projections},
we have the equality
\( \{ p^\alpha_\gamma \in A^\alpha \}
=  \{ p^\beta _\gamma \in A^\beta  \}
\).
In other words, if two events of~$\Sigma^A_0$ are equal,
then they are pullbacks of equal events in some common~$\Sigma^\gamma$.
We can therefore define an additive probability~$P_0$ on~$\Sigma^A_0$
by \( P_0(p^\alpha \in A^\alpha) = \mu^\alpha(A^\alpha) \).
To use the Carathéodory extension theorem,
we must only check \sig additivity of~$P_0$,
equivalently that if \( A^A_1 \supseteq A^A_2 \supseteq \dotsb \)
and \( P_0(A^A_n) \ge \epsilon > 0 \)
then \( \bigcap_n A^A_n \ne \emptyset \).

By definition \( A^A_n = \{ p^{\alpha_n} \in A^{\alpha_n} \} \).
By taking preimages we can suppose \( \alpha_1 \le \alpha_2 \le \dotsb\, \).
%Since the~$p^{\alpha_n}$ are surjective,
We obtain a sequence of \( A^{\alpha_n} \subseteq S^{\alpha_n} \)
such that
%\( p^{\alpha_n}_{\alpha_{n+1}}(A^{\alpha_{n+1}}) \subseteq A^{\alpha_n} \).
\( \mu^{\alpha_n}(A^{\alpha_n}) = P_0(A^A_n) \ge \epsilon > 0 \).
By inner regularity,
there are compact sets \( C^{\alpha_n} \subseteq A^{\alpha_n} \)
so that \( \mu^{\alpha_n}(A^{\alpha_n} \setminus C^{\alpha_n}) \)
be arbitrarily small.
Setting \( K^{\alpha_n} =
\bigcap_{k\le n} \{p^{\alpha_k}_{\alpha_n} \in C^{\alpha_k}\} \bigr) \),
we can in particular impose
\(  \mu^{\alpha_n}(A^{\alpha_n} \setminus K^{\alpha_n})
\le \sum_{k\le n} \mu^{\alpha_k}(A^{\alpha_k} \setminus C^{\alpha_k})
<   \epsilon/2
\) for all~$n$,
so that \( \mu^{\alpha_n}(K^{\alpha_n}) \ge \epsilon/2 > 0 \)
and \( K^{\alpha_n} \ne \emptyset \).
Since $K^{\alpha_n}$ is the intersection of~$C^{\alpha_n}$
and closed sets,
$K^{\alpha_n}$ is compact.
Furthermore \( p^{\alpha_n}_{\alpha_{n+1}}(K^{\alpha_{n+1}})
\subseteq K^{\alpha_n} \).
